Corrections

### 2020-10-26 new_paper.tex
Add refs inside the reply tex

In the inverse problems community, work is mostly computational and
less theoretic. Model errors were considered in \cite{Attia20,
  Koval20}. The former study is focused on inferring of a Quantity of
Interest (QoI). The focus of the latter is reducing forward solves,
using randomized linear algebra. Both studies present numerical
techniques for finding optimal designs when model error is
present. Both are restricted to linear inverse problems (although in
the latter the authors use their method on a nonlinear problem with a
Laplace approximation for the posterior). Both find an optimal design
by first solving a continuous problem for sensor weights. Said
solution is then sparsified to give a binary design. Both studies are
successful in the task of Bayesian inversion. However, neither of
these studies mentions any effect model errors can have on sensor
clusterization. The current study is mostly theoretical and aims to
fill the theoretical gap of understanding sensor clusterization.

@@

\subsection{D-Optimal Designs in Infinite Dimensions}\label{subsec:D optimal design} 
A D-optimal design maximizes expected KL divergence between posterior
and prior. It is useful to recall the definition of KL divergence for
an arbitrary prior measure:
$$
KL(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(x) \der \post(x).
$$

@@

\section{Acknowledgements}
This study is a part of my PhD thesis. It was written under the
instruction of Prof. Georg Stadler in New York University's Courant
Institute. I would like to thank him for his great mentorship.

>>>>

In the inverse problems community, work is mostly computational and
less theoretic. Model errors were considered in \cite{Attia20,
  Koval20}. The former study is focused on inferring of a Quantity of
Interest (QoI). The focus of the latter is reducing forward solves,
using randomized linear algebra. Both studies present numerical
techniques for finding optimal designs when model error is
present. Both are restricted to linear inverse problems (although in
the latter the authors use their method on a nonlinear problem by
taking a Laplace approximation for the posterior). Both find an
optimal design by first solving a continuous problem for sensor
weights. Said solution is then sparsified to give a binary
design. Both studies are successful in the task of Bayesian
inversion. However, neither of these studies mentions any effect model
errors can have on sensor clusterization. The current study is mostly
theoretical and aims to fill the theoretical gap of understanding
sensor clusterization.

@@

\subsection{D-Optimal Designs in Infinite Dimensions}\label{subsec:D optimal design} 
A D-optimal design maximizes expected KL divergence between posterior
and prior. It is useful to recall the definition of KL divergence for
an arbitrary prior measure:
$$
KL(\post||\pr) = \int \log \frac{\der \post}{\der \pr}(\param) \der \post(\param).
$$

@@

\section{Acknowledgements}
This study is a part of my PhD thesis. Most of it was written under
the instruction of Prof. Georg Stadler in New York University's
Courant Institute. I would like to thank him for his great
mentorship. This work was supported by The Raymond and Beverly Sackler
Post-Doctoral Scholarship.

### 2020-10-26 reply.tex
Cite karina and ahmed, changed propostions, theorems, lemmas to upper/lowercase, discarded the requirement for zero mean
Add refs inside the reply tex

\documentclass{amsart}
\input{definitions}

\title{Corrections}

@@

Both referees made great comments that I feel improve the manuscript
substantially, and I would like to thank them for that. I followed up
on every point made. The referees' comments and my replies are listed
below. Again, thank you for taking the time and helping me improve
this manuscript.

@@

\item On page 10, figure 2 and section 4.2 deliver the main conclusion of
the article. These areas are deficient with only brief descriptions,
and should be much more thoroughly explained. In particular page 10,
lines 38-39 "If the precision in these is lower than the precision for
the next eigenvector, a repeated measurement is optimal" needs to be
elaborated on. How do you come to this conclusion? Additionally, the
wording of the statement can lead to confusion. From figure 2, it
looks like all measurements grant less precision than that of the
fourth eigenvector, so I first interpret this as all measurements
should be repeated. I believe these issues can be fixed by significant
elaboration in section 4.2.
\end{enumerate}

@@

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{Moved the equation after $\Sigma$ is defined.}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0?  \ydnote{Assuming zero mean
    is hardly necessary, so I removed this statement.}

@@

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective
  function.
  \ydnote{Added comment before statment of theorem where $\tar$ first
    appears. Also, I added a formal definition of D-optimal design
    just after the theorem.}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded.
  \ydnote{Rephrased and added a short explanation.}

@@

This article discusses D-optimal experimental design for infinite
dimensional Bayesian linear inverse problems, and attempts to provide
a mathematical foundation to understanding the issue of clusterization
in such scenario, i.e., finding D-optimal designs.  As the author
mentioned in the Acknowledgments Section, the paper is paper is part
of the Ph.D. dissertation, and in general provides a good prospective
to sensor placement for Bayesian linear inverse problems formulated
using infinite dimensional approach.  I regret, however, to say that
the paper requires a major revision before being considered for
publication.  Below, I provide some comments, that hopefully will help
improve the manuscript.  Also, provided are some recent references,
the author may find useful.

@@

The author should clearly state why one should consider
infinite-dimensional formulation of the observation operator? One
could just merge the observation operator into the forward simulation
operator, and follow standard formulations adopted by the works in the
references below. Moreover, when it comes to sensor placement,
observations are almost surely pointwise in space/time. In this case,
I don't see the benefit of consider infinite-dimensional formulation.
\ydnote{I was not able to arrive at the same results when the forward
  and observation operators were merged. A short remark on this was
  added. It is placed after equation (2.5). Specifically, we need it
  in equation (3.1).}

@@

On page 8, Equation 4.2, which is crucial in this study, assumes that
the forward operator is invertible. This is clearly impossible in
practical Bayesian inverse problems, otherwise, it reduces to a
standard regression problem. This is understandable for clarification,
however, the following argument on Page 9 that extends this assumption
is not well-justified.
\ydnote{This is a great point! The flawed explanation was removed. I
  was able to remove that assumption, at the cost of changing several
  claims in the paper. Mainly, it forced me to work with Hilbert
  spaces everywhere. I believe this is for the best, because
  considering Banach spaces did not add much.}

@@

A numerical example with the setup studied in the paper, should help
clarify several confusions that a reader can fall for easily.
\ydnote{I added several plots that I believe make the arguments and
  conclusions clearer. I also added an illustration story with
  graduated lab cylinders. I also added a theorem summarizing the
  results for vanishing model error.}

@@

In the abstract (line 20, page 1), and on page 5, lines 30-40, the
author mentions that the effect of observation-correlations on sensor
clusterization will be considered later, but I failed to find any
relevant discussion to that issue which I find interesting.
\ydnote{The discussion on observation correlation and how it mitigates
  clusterization can be found in the last section. It is now stated
  clearly in the contributions section.}

@@

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc.  \ydnote{All such bad references and links were fixed.}

@@

Sensor clusterization in OED is central to this study. Figure 2 is
used to illustrate the phenomena, however, it is underrepresented, and
is hard to decipher. Specifically, Section 4.2 (Page 10, lines 36-39),
and caption of Figure 2 should be rewritten with clear explanation of
the axes, and the plot-generation process.
%
\ydnote{I extended the
  discussion relating to clusterization, added another plot and
  explained how they arise.}

@@

Page 6; in equation 2.7, don't you need an expectation over all priors
to achieve this result? Please clarify.
%
\ydnote{The expectation / integration over the prior space happens
  inside the KL divergence:
  $$
  \mathbb{E}_{\data}[KL(\post||\pr)] = \int KL(\post||\pr) \der
  \mu(\data) = \int \int \log \frac{\der \post}{\der \pr}(x) \der
  \post(x) \der \mu(\data)
  $$
  where $\mu(\data)$ is the distribution of data (usually called
  evidence). I improved the notation to reflect the dependence of the
  posterior on the data $\data$. I added above definition of KL
  divergence to the manuscript.}

Page 6, line 13; the optimization problem is solved for $\mathcal{O}$,
not $\Psi$ ?  \ydnote{This line was unclear. I extended the
  explanation. The mauscript now reflects the claim that the optimal
  $\obs^{\star}$ is the maximizer of $\tar(\obs)$.}

@@

page 6, In the proof of Lemma 3.1, the author utilized the operator
$T$, which is only introduced in the appendix (Proof of Lemma
A.1). Maybe state that clearly here. Also, in the proof, from step 4
to 5, the first and third terms vanished; why?
%
\ydnote{This point is spot on. I added the definition of $T$ before
  the derivation. The proof referee 2 refers to is not the proof of
  Lemma 3.1. It is the first variation of the objective. I reworded a
  few sentences to make this clearer. Regarding the vanishing terms
  --- this is done using trace rules (notice the $\frac{1}{2}$
  prefactor disappears). I added a comment explaining this.}

Page 7; Proposition 1 should be replaced with something like
Proposition 3.2 or something similar to match previous referencing
(e.g., Lemma 3.1). \ydnote{Fixed.}

Page 7, line 27 (and also line 31); the reference to Proposition 2
seems to be incorrect. Also, state clearly which appendix the proof is
delegated to.  \ydnote{Fixed.}

Page 10, Corollary 1 should be renamed (see the comment on Proposition
1 above). Same applies to Corollary 3 in the appendix. Better also to
clarify which appendix. Finally, the author utilizes
$\widehat{\Gamma_{post}}$ int the corollary, which is defined only in
the appendix, under the proof. \ydnote{All comments on numbering and
  references are great and correct. All were fixed. I added an
  explanation of what $\widehat{\Gamma_{post}}$ means where it
  appears.}

Page 11, in the proof of Lemma A.1 (lines 39-43), the partial
derivative vanished from step 2 to step 3; please explain!
\ydnote{I added an extra equality line for explanation.}

>>>>

\documentclass{amsart}
\input{definitions}
\usepackage{xr}
\externaldocument{new_paper}
\title{Corrections}

@@

Both referees made great comments that I feel improve the manuscript
substantially, and I would like to thank them for that. I followed up
on every point made. The referees' comments and my replies are listed
below. Again, thank you for taking the time and helping me improve
this manuscript. Below, when I refer to an item - it refers to the new
version of the paper.

@@

\item On page 10, figure 2 and section 4.2 deliver the main conclusion of
the article. These areas are deficient with only brief descriptions,
and should be much more thoroughly explained. In particular page 10,
lines 38-39 "If the precision in these is lower than the precision for
the next eigenvector, a repeated measurement is optimal" needs to be
elaborated on. How do you come to this conclusion? Additionally, the
wording of the statement can lead to confusion. From figure 2, it
looks like all measurements grant less precision than that of the
fourth eigenvector, so I first interpret this as all measurements
should be repeated. I believe these issues can be fixed by significant
elaboration in section 4.2.
%
\ydnote{I added figure \ref{fig:optimal vs not} prior to figure
  \ref{fig:clusterization}. I also added Theorem \ref{thm:char}, which
  neatly summarizes the results of section
  \ref{section:vanishing}. This should help understand section
  \ref{section:clusterization}, which was extended and modified
  heavily.}
\end{enumerate}

@@

\item Page 4, Line 14: In equation (2.1), $\Sigma$ has not been
  defined. Please formally define this before giving the equation.
  \ydnote{Moved this equation to after $\Sigma$ is defined.}

\item Page 4, Line 21: The prior distribution $\mathcal{N}(0,
  \Gamma_{pr})$ assumes the prior mean is 0. This is worthy of some
  comment. Why must the prior mean be 0?
  %
  \ydnote{Great point. Assuming zero mean is hardly necessary, so I
  removed this statement.}

@@

\item Page 6, Line 7: Please describe what $\psi$ is in the
  theorem. It is defined mathematically but not described. Only much
  later is it stated that this is the objective function.
  \ydnote{Added comment before statment of theorem where $\tar$ first
    appears. I also added a definition of KL divergence in the
    beginning of section \ref{subsec:D optimal design}. I added
    Definition \ref{def:d optimality} which formally defines
    D-optimality.}

\item Page 6, Line 19-20: "In section 3.2 we relax the constraints on
  $\mathcal{O}$ so that the optimization problem in (3.1) and find
  gradients for the new constraints." This sentence is unclear and
  should be reworded.
  \ydnote{Rephrased and added an explanation.}

@@

This article discusses D-optimal experimental design for infinite
dimensional Bayesian linear inverse problems, and attempts to provide
a mathematical foundation to understanding the issue of clusterization
in such scenario, i.e., finding D-optimal designs.  As the author
mentioned in the Acknowledgments Section, the paper is paper is part
of the Ph.D. dissertation, and in general provides a good prospective
to sensor placement for Bayesian linear inverse problems formulated
using infinite dimensional approach.  I regret, however, to say that
the paper requires a major revision before being considered for
publication.  Below, I provide some comments, that hopefully will help
improve the manuscript.  Also, provided are some recent references,
the author may find useful.
%
\ydnote{The references are much appreciated. I extended the ``related
  work'' section accordingly.}

@@

The author should clearly state why one should consider
infinite-dimensional formulation of the observation operator? One
could just merge the observation operator into the forward simulation
operator, and follow standard formulations adopted by the works in the
references below. Moreover, when it comes to sensor placement,
observations are almost surely pointwise in space/time. In this case,
I don't see the benefit of consider infinite-dimensional formulation.
%
\ydnote{I was not able to arrive at the same results when the forward
  and observation operators were merged. A short remark on this was
  added. It is placed just before section
  \eqref{subsec:dynamics}. Specifically, we need it in (e.g.)
  \eqref{eq:mod conditions}.}

@@

On page 8, Equation 4.2, which is crucial in this study, assumes that
the forward operator is invertible. This is clearly impossible in
practical Bayesian inverse problems, otherwise, it reduces to a
standard regression problem. This is understandable for clarification,
however, the following argument on Page 9 that extends this assumption
is not well-justified.
%
\ydnote{This is a great point! The flawed explanation was removed. I
  was able to remove that assumption, at the cost of changing several
  claims in the paper. Mainly, it forced me to work with Hilbert
  spaces everywhere. I believe this is for the best, because
  considering Banach spaces did not add much. The new derivations
  appear in \eqref{eq:pre manipulations} and \eqref{eq:mod
    objective}. Instead, I use the much more reaonable assumption that
  $\fwd \prcov \fwd^*$ is invertible.}

@@

A numerical example with the setup studied in the paper, should help
clarify several confusions that a reader can fall for easily.
\ydnote{I added several plots that I believe make the arguments and
  conclusions clearer. I added Theorem \ref{thm:char}, summarizing the
  results for vanishing model error. I also added an illustration
  story with graduated lab cylinders, just before the statement of
  Theorem \ref{thm:char} (see also figure \ref{fig:cylinder}).}

@@

In the abstract (line 20, page 1), and on page 5, lines 30-40, the
author mentions that the effect of observation-correlations on sensor
clusterization will be considered later, but I failed to find any
relevant discussion to that issue which I find interesting.
%
\ydnote{The discussion on observation correlation and how it mitigates
  clusterization can be found in section \ref{section:non
    vanishing}. It is now stated clearly in the contributions
  section.}

@@

I found it difficult to trace the referenced Lemmas, Corollaries,
etc., mainly because bad referencing in the appendix, and the links do
not works properly.  For example Corollary 2 should be Corollary B.x,
etc.
%
\ydnote{All such bad references and links were fixed.}

@@

Sensor clusterization in OED is central to this study. Figure 2 is
used to illustrate the phenomena, however, it is underrepresented, and
is hard to decipher. Specifically, Section 4.2 (Page 10, lines 36-39),
and caption of Figure 2 should be rewritten with clear explanation of
the axes, and the plot-generation process.
%
\ydnote{I extended the discussion relating to clusterization. I added
  figure \ref{fig:optimal vs not} to illustrate how the posterior of a
  D-optimal design behaves. Then I extend the discussion to section
  \ref{section:clusterization}.}

@@

Page 6; in equation 2.7, don't you need an expectation over all priors
to achieve this result? Please clarify.
%
\ydnote{The expectation / integration over the prior space happens
  inside the KL divergence:
  $$
  \mathbb{E}_{\data}[KL(\post||\pr)] = \int KL(\post||\pr) \der
  \mu(\data) = \int \int \log \frac{\der \post}{\der \pr}(\param) \der
  \post(\param) \der \mu(\data)
  $$
  where $\mu(\data)$ is the distribution of data (usually called
  evidence). I improved the notation to reflect the dependence of the
  posterior on the data $\data$. I added above definition of KL
  divergence to the beginning of section \ref{subsec:D optimal design}.}

Page 6, line 13; the optimization problem is solved for $\mathcal{O}$,
not $\Psi$ ?  \ydnote{This line was unclear. I extended the
  explanation. The mauscript now reflects the claim that the optimal
  $\obs^{\star}$ is the maximizer of $\tar(\obs)$. This is recorded
  explicitly in Definition \ref{def:d optimality}.}

@@

page 6, In the proof of Lemma 3.1, the author utilized the operator
$T$, which is only introduced in the appendix (Proof of Lemma
A.1). Maybe state that clearly here. Also, in the proof, from step 4
to 5, the first and third terms vanished; why?
%
\ydnote{This point is spot on. I added the definition of $T$ before
  the derivation, just after the statment of Lemma
  \ref{lemma:lax}. The proof referee 2 refers to is not the proof of
  Lemma 3.1. It is the first variation of the objective. I reworded a
  few sentences to make this clearer. Regarding the vanishing terms
  --- this is done using trace rules (notice the $\frac{1}{2}$
  prefactor disappears). I added a comment explaining this.}

Page 7; Proposition 1 should be replaced with something like
Proposition 3.2 or something similar to match previous referencing
(e.g., Lemma 3.1).
%
\ydnote{Fixed.}

Page 7, line 27 (and also line 31); the reference to Proposition 2
seems to be incorrect. Also, state clearly which appendix the proof is
delegated to.
%
\ydnote{Fixed.}

Page 10, Corollary 1 should be renamed (see the comment on Proposition
1 above). Same applies to Corollary 3 in the appendix. Better also to
clarify which appendix. Finally, the author utilizes
$\widehat{\Gamma_{post}}$ int the corollary, which is defined only in
the appendix, under the proof.
%
\ydnote{All comments on numbering and references are great and
  correct. All were fixed. I added an explanation of what
  $\widehat{\Gamma_{post}}$ means before Corollary \ref{cor:same
    meas}.}

Page 11, in the proof of Lemma A.1 (lines 39-43), the partial
derivative vanished from step 2 to step 3; please explain!
%
\ydnote{I added an extra equality line for explanation in the proof of
  lemma \ref{lemma:lax}.}
